\documentclass[a4paper,10pt]{article}

% --- PACKAGES ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{titlesec}

% --- DOCUMENT SETUP ---
\geometry{top=1.0cm, bottom=1.0cm, left=1.0cm, right=1.0cm}

\pagestyle{empty}

\hypersetup{
    pdftitle={CV Murilo Alves Alborghette},
    pdfauthor={Murilo Alves Alborghette},
    colorlinks=true,
    linkcolor=black,
    urlcolor=black
}

\setcounter{secnumdepth}{0}

\titleformat{\section}
{\Large\bfseries}
{}
{0em}
{}
[\titlerule\vspace{0.5ex}]

\begin{document}

% --- HEADER ---
\begin{center}
{\LARGE \textbf{Murilo Alves Alborghette}}

Senior iOS Software Engineer | Swift | SwiftUI | Mobile Architecture | Fintech
\end{center}

Campinas, Brazil \\
\href{mailto:murilo.alves@outlook.com}{murilo.alves@outlook.com} \\
\href{https://www.linkedin.com/in/murilo-alves-alborghette-43b37829}{linkedin.com/in/murilo-alves-alborghette-43b37829}

% --- SUMMARY ---

\section{Summary}

Senior iOS Software Engineer with 10+ years of software development experience and 9+ years specializing in iOS platforms. Experienced in building scalable mobile applications using Swift, Objective-C, SwiftUI, UIKit, and modern architectural patterns such as MVVM and Clean Architecture. Proven track record delivering high-impact mobile solutions in fintech, e-commerce, and edtech environments, while collaborating closely with product, design, and backend teams. Experienced in modernizing legacy codebases, improving development workflows, and mentoring mobile engineers.

% --- EXPERIENCE ---

\section{Experience}

\subsection*{\textbf{Stone} \hfill Remote, Brazil}
\textit{Senior iOS Software Engineer / Mobile Tech Lead \hfill Mar 2024 – Present}

\begin{itemize}

\item Led mobile development in the Credit Revitalization squad, delivering new credit solutions that doubled the number of clients using credit products in the mobile application.

\item Mentored two mobile developers while coordinating mobile releases and ensuring code quality across the team.

\item Led the migration of legacy user flows from UIKit to SwiftUI, improving UI scalability and reducing maintenance complexity.

\item Implemented shared business logic using Kotlin Multiplatform (KMP), enabling code reuse across Android and iOS platforms.

\item Acted as Code Owner for mobile repositories, reviewing and approving pull requests and ensuring adherence to architectural standards.

\end{itemize}

\subsection*{\textbf{Banco Itaú} \hfill Remote, Brazil}
\textit{Senior iOS Software Engineer \hfill Nov 2022 – Mar 2024}

\begin{itemize}

\item Delivered a redesigned bank statement experience in the Itaú super app, reducing screen load time by 25\% and improving user experience.

\item Developed new features in the ``My Finances'' section, helping users better understand spending behavior and financial activity.

\item Collaborated with product managers, designers, and backend teams to deliver scalable mobile solutions aligned with business goals.

\end{itemize}

\subsection*{\textbf{MovilePay (iFood Pago)} \hfill Remote, Brazil}
\textit{Senior iOS Software Engineer \hfill Feb 2022 – Nov 2022}

\begin{itemize}

\item Contributed to the development of credit solutions tailored for iFood partners and merchants.

\item Built scalable features following the Clean Swift (VIP) architecture to support maintainable and testable mobile modules.

\item Implemented automated tests and CI pipelines to ensure application reliability and release stability.

\end{itemize}

\subsection*{\textbf{CI\&T} \hfill Campinas, Brazil}
\textit{Senior iOS Software Engineer \hfill Aug 2017 – Feb 2022}

\begin{itemize}

\item Delivered mobile solutions for e-commerce, fintech, and healthcare applications across multiple client projects.

\item Mentored and trained more than 10 developers in iOS development practices, helping expand the company’s mobile engineering capabilities.

\item Collaborated with cross-functional teams in Agile environments to deliver high-quality mobile applications.

\end{itemize}

\subsection*{\textbf{Somos Educação} \hfill Bauru, Brazil}
\textit{iOS Developer / Tech Lead \hfill Feb 2016 – Aug 2017}

\begin{itemize}

\item Led development of the Adapta/Plurall classroom orchestration mobile application used in digital education environments.

\item Implemented CI/CD pipelines with Jenkins and Fastlane to automate testing and App Store releases.

\item Maintained a modular project architecture with automated build and release processes.

\end{itemize}

\subsection*{\textbf{MStech} \hfill Bauru, Brazil}
\textit{Front-End Developer / iOS Developer \hfill Dec 2011 – Jan 2016}

\begin{itemize}

\item Built the company’s first iOS application (Livrera), a digital bookshelf application for educational content.

\item Managed the full mobile app lifecycle from feature planning to beta testing and App Store release.

\item Developed educational games and interactive applications using ActionScript, JavaScript, and HTML.

\end{itemize}

\subsection*{\textbf{Lecom} \hfill Bauru, Brazil}
\textit{Java Developer \hfill Feb 2010 – Dec 2011}

\begin{itemize}

\item Developed web applications using Java, Spring Boot, and MySQL.

\item Maintained CRM and Sales Force systems, implementing new features and supporting existing modules.

\end{itemize}

% --- SKILLS ---

\section{Skills}

\begin{itemize}

\item \textbf{Languages:} Swift, Objective-C, Kotlin, C\#, Java, JavaScript, Python

\item \textbf{iOS Development:} SwiftUI, UIKit, CoreData, GCD, XCTest, XCUITest, App Store Guidelines

\item \textbf{Architecture:} MVVM, MVVM-C, MVC, VIP (Clean Swift), MVP

\item \textbf{Tools:} Git, Fastlane, GitHub Actions, Jenkins, CocoaPods, Carthage, Swift Package Manager, XcodeGen

\item \textbf{Other:} Kotlin Multiplatform (KMP), Android, CI/CD, Mobile Architecture

\item \textbf{Languages:} Portuguese (Native), English (Professional)

\end{itemize}

% --- EDUCATION ---

\section{Education}

\subsection*{\textbf{Faculdade G\&P} \hfill Pederneiras, Brazil}
\textit{B.Sc. Computer Information Systems \hfill 2011 – 2014}

\end{document}
